\documentclass{article}
\usepackage{authblk}
\usepackage{vhistory}
\begin{document}

\title{Team Agreement for Group H}
\author[1]{Konstantinos Poumpouridis}
\date{15 feb 2023}
\author[2]{Dean van Deijck}
\author[3]{Konstantin Malevski}
\author[4]{Floris Heije}
\author[5]{Petar Boychev}
\affil[1]{Project leader, Note taker}
\affil[2]{Product Owner}
\affil[3]{Development Team, Note taker}
\affil[4]{Development Team}
\affil[5]{Development Team}

\maketitle
\newpage

\begin{versionhistory}
    \vhEntry{0.1}{15.02.23}{Poumpouridis}{Creation}
    \vhEntry{0.2}{16.02.23}{Poumpouridis}{Added Note taker, Fixed the date}
\end{versionhistory}

\newpage
\section{Introduction}

This document outlines the agreement for our Group H. The goal of this agreement is to provide a clear understanding of our roles, responsibilities, and expectations for effective collaboration and efficient work processes.

\section{Roles and Responsibilities}

\subsection{Scrum Master: Konstantinos Poumpouridis}
\begin{itemize}
    \item Facilitates Scrum meetings and ceremonies
    \item Ensures team members follow Scrum framework and practices
    \item Removes impediments and blockers that affect team productivity
\end{itemize}

\subsection{Note taker: Konstantinos Poumpouridis, Konstantin Malevski}
\begin{itemize}
    \item Taking notes while Scruming
    \item Ensures that the notes were taken during coach hours
    \item Is responsible for weekly notes
\end{itemize}

\subsection{Product Owner: Dean van Deijck}
\begin{itemize}
    \item Defines product vision and goals
    \item Prioritizes product backlog items
    \item Ensures the team delivers high-quality and valuable products
\end{itemize}

\subsection{Development Team: Konstantin Malevski, Petar Boychev, Floris Heije}
\begin{itemize}
    \item Develops and delivers product increments in Sprints
    \item Collaborates with the Scrum Master and Product Owner
    \item Follows agreed-upon technical standards and quality requirements
\end{itemize}
\newpage
\section{Communication and Collaboration}

\subsection{Communication}
\begin{itemize}
    \item All team members must attend and actively participate in daily Scrum meetings.
    \item Meetings will be held via [Discord/Teams].
    \item Communication must be respectful and professional.
    \item Use the Trello Board to share updates, progress, and blockers.
\end{itemize}

\subsection{Collaboration}
\begin{itemize}
    \item All team members must collaborate on tasks and work together to complete Sprints.
    \item If a team member is unable to complete a task, they should communicate with the Scrum Master and Product Owner immediately.
    \item The team must review and discuss completed work before marking it as done.
\end{itemize}

\section{Sanctions}

\subsection{Failure to comply with the team agreement will result in sanctions.}
\subsection{Sanctions will be decided by the team as a whole and will not involve monetary fines.}
\subsection{Sanctions may include but are not limited to the following:}
\begin{itemize}
    \item Loss of voting rights in team meetings
    \item Removal from certain tasks or roles
    \item Required attendance in additional meetings to discuss progress and blockers
\end{itemize}

\section{Conclusion}

By agreeing to this team agreement, we commit to working together effectively, communicating respectfully, and collaborating to deliver high-quality products. We understand that failure to comply with this agreement may result in sanctions.

\end{document}
