\documentclass{article}
\title{Personal Specialisation Project: Plan of Action}
\author{Konstantinos Poumpouridis}
\date{16/05/2023}
\pagenumbering{arabic}
\maketitle
\thispagestyle{empty}
\newpage
\begin{document}



\section{Objective}
The objective is to prove that I can run macOS on non-Apple Devices and Xcode, Which is exclusive to Mac devices.
\section{Tasks}

List the tasks that must be completed to achieve the objective.

\begin{enumerate}
\item Find legit macOS rom
\item Have working EFI files
\item Make it stable and can run without any issues
\item Try and run Xcode on the device
\end{enumerate}

\section{Timeline}

Provide a timeline for completing each task.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|}
\hline
\textbf{Task} & \textbf{Deadline} \\
\hline
Create plan of action & 17th May \\
Create proof of concept & 19th May \\
Final version of Documentation & 24th May \\
\hline
\end{tabular}
\end{table}

Section{Research questions}

\section{Main question}
\textit{Is Hackintosh worth it?}

\subsection{Sub questions}
\begin{enumerate}
    \item Is it easy to build your own Hackintosh?
    \item Are all components compatible with Hackintosh?
    \item Are there limitations?
\end{enumerate}
\newpage
\section{Resources}

List any resources that will be needed to complete the tasks.

\begin{itemize}
\item My old laptop (MSI GF64 3RC)
\item Open Core EFI folder (To make it bootable)
\item DMG file of macOS
\item Guide and forums for compiling my own macOS
\end{itemize}

\section{Potential Risks}

Identify any potential risks or obstacles that could affect the completion of the plan.

\begin{itemize}
\item My test laptop can brick or be damaged while installing
\item My Apple ID can be blocked
\item I get a cease-and-desist from Apple
\end{itemize}

\section{Contingency Plan}

Provide a contingency plan for addressing any potential risks or obstacles.

\begin{itemize}
\item If I have issues compiling my own EFI than I can copy a template to make it bootable
\item Second option is always to run on a VM
\item And as last option is to do PCI passthrough with KVM.
\end{itemize}

\end{document}