\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\title{PVI Proposal}
\author{Konstantinos Poumpouridis}
\date{08/02/2023}
\pagenumbering{arabic}
\begin{document}
\maketitle
\thispagestyle{empty}
    
\newpage
\section{Changelog}
    \begin{table}[htbp]
        \begin{tabular}{|l|l|l|}
            \hline
            Version & Changes         & Date   \tabularnewline \hline
            0.1     & Initial version & 24/03/23 \tabularnewline \hline
        \end{tabular}
    \end{table}
\newpage
\tableofcontents
\newpage
\section{Introduction}
In this report, I'll be researching a vulnerability and investigating it for my personal project. This proposal was meant to show the teachers what I'm planning to do for my personal project. Starting with the Problem, Objectives, Scope, Methodology and Conclusion.
\section{Problem}
In This research, we'll be discussing the vulnerabilities of our FRITZ!Box. Since FRITZ!Box never updates its features to the new standards. At least the FRITZ!Box 5490 doesn't get any new features from 7590 AX. This means that my FRITZ!Box is running with an SMB V1 which is unsafe by today's standards.
\subsection{Main research question}
What is the impact of these vulnerabilities on the security of FRITZ!Box and its users?

\subsection{Sub research questions}
\begin{enumerate}
    \item How does the vulnerabilities affect the confidentiality, integrity, and availability of FRITZ!Box and FRITZ!Box NAS?
    \item What are the most common types of SMB V1 
    \item Can vulnerability cause more damage to the rest of FRITZ!Box?
    \item What can AVM (The factory) do to mitigate or prevent this?
\end{enumerate}
\section{Objectives}
The main objectives of this investigation are:
\begin{itemize}
    \item To identify vulnerabilities.
    \item To determine how much damage it can cause.
    \item To recommend preventing this vulnerability 
\end{itemize}
\section{Scope}
This investigation will be focused on a specific network and system. The investigation will cover the following areas:
\begin{itemize}
    \item Network security
    \item Application security
    \item System's security
\end{itemize}
\section{Methodology}
The investigation will be conducted using a combination of automated tools and manual techniques. The following methodology will be employed:
\begin{itemize}
    \item Footprinting: To gather information about our FRITZ!Box.
    \item Scanning: To scan for open ports or to find any openings for a vulnerability
    \item Pen testing: This involves testing for any possible penetration to exploit any vulnerabilities.
    \item Reporting: The document will be created with the report on the pen-testing alongside the research questions and how to prevent it in Dot Framework.
\end{itemize}
\section{Conclusion}
In conclusion, this proposal is about how the features need to be updated or deprecated for any further use. With future demonstrations about this Personal Project, I want to show my class and my group what great alternatives are and how to best mitigate this.
\end{document}